Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
removing formulae for P/R, condensing discussion into conclusions for space

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and build integration success.

@@

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, providing further evidence that social factors
importantly predict build success.

@@

\subsection{Summary}

Social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after downsampling. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be as
scrutinized as core team member commits before the integration build tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with 1000+ followers were more than a 10\% more succesful in their
builds as compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

Overall, although experience is an imperfect indicator, but
experienced developers appear more likely to make high quality commits.

\section{Threats to validity}

@@

We have also found that being a core contributor and having a large follower
base can be an indicator of build integration success.
These results provide evidence that more experienced
developers are more likely to generate a high quality contribution.

>>>>

In Section~\ref{sec:successClassification} we discuss the build classification
success rate for the technical and social factors.  In Section~\ref{sec:core},
we compare the build success rate of core project members to non-core project
members.  In Section~\ref{sec:followerSuccess}, we compare the relationship
between a developer's followers and build integration success. We conclude the
section with a discussion of threats to validity (Section~\ref{sec-threats}).

@@

Note also that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic accounts
for the accuracy of the model's predictive power. It is more
robust than \textit{correctly classified} instances alone, since it takes into account the
correctly guessed instances occurring by chance. The precision, recall and
F-measure are calculated over the successful and unsuccessful classes and then
averaged (standard procedure in Weka).  All these measures increase with social
data in the feature space, making the prediction more reliable. The mean absolute error
decreases in both cases, further subtantiating the importance of social factors
in predicting build success.

@@

\subsection{Threats to validity}
\label{sec-threats}

@@

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction.  While the increase was noticeable 
with the full data set, there was a much greater increase in prediction
accuracy after downsampling. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be as
scrutinized as core team member commits before the integration build tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with 1000+ followers were more than a 10\% more succesful in their
builds as compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

Although experience is an imperfect indicator, 
experienced developers appear more likely to make high quality commits.
